---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 300
)
```

# Dynamic Zoning

<!-- badges: start -->
`r badger::badge_lifecycle("experimental")` `r badger::badge_repostatus("Active")`
<!-- badges: end -->

The goal of dz is to showcase algorithms developed to handle dynamic zoning applications for the team-orienteering problem.

## Installation

You can install the development version of dz from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Rosenkrands/dz")
```

We can then load the library with the following command:

```{r load_library}
library(dz)
```


## Test instances

There are 7 seven test instances included in the package.
They can be accessed with `dz::test_instances`.
```{r number_of_test_instances}
length(test_instances)
```

```{r plot_test_instance}
plot(test_instances$p7_chao, delaunay = F, voronoi = F)
```

## Clustering

With the `clustering` function we are able to decompose an instance into a number of disjoint sets (disregarding the source node).

```{r perform_clustering}
clust <- clustering(
  inst = test_instances$p7_chao,
  k = 4,
  cluster_method = "pam"
)

plot(clust)
```
## Routing

Given the an instance with clusters we are able to find a set of routes using the `routing` function.

```{r perform_routing}
rout <- routing(
  clust = clust,
  routing_method = "random"
)

plot(rout)
```
