---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 300
)
```

# Dynamic Zoning

<!-- badges: start -->
`r badger::badge_lifecycle("experimental")` `r badger::badge_repostatus("Active")`
<!-- badges: end -->

The goal of dz is to showcase algorithms developed to handle dynamic zoning applications for the team-orienteering problem.

## Installation

You can install the development version of dz from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Rosenkrands/dz")
```

We can then load the library with the following command:

```{r}
library(dz)
```


## Test instances

There are 7 seven test instances included in the package.
They can be accessed with `dz::test_instances`.
```{r}
length(test_instances)
```

```{r}
plot(test_instances$p1_tsiligirides, delaunay = T, voronoi = T)
```
